Hooded broadcast sprayer for particle drift reduction

### 2021-09-01 supp_file/supplemental_file.Rmd
,m

| Bayes Factor  | Interpretation               	|
|--------------	|------------------------------	|
| > 100        	| Extreme evidence for H~1~     	|
| 30 – 100     	| Very strong evidence for H~1~ 	|
| 10 – 30      	| Strong evidence for H~1~      	|
| 3 – 10       	| Moderate evidence for H~1~    	|
| 1 – 3        	| Anecdotal evidence for H~0~    	|
| 1            	| No evidence                  	|
| 1/3 – 1      	| Anecdotal evidence for H~0~   	|
| 1/3 – 1/10   	| Moderate evidence for H~0~    	|
| 1/10 – 1/30  	| Strong evidence for H~0~      	|
| 1/30 – 1/100 	| Very strong evidence for H~0~ 	|
| < 1/100      	| Extreme evidence for H~0~     	|

>>>>

| Bayes Factor  | Interpretation               	|
|--------------	|------------------------------	|
| > 100        	| Extreme evidence for H~1~     	|
| 30 – 100     	| Very strong evidence for H~1~ 	|
| 10 – 30      	| Strong evidence for H~1~      	|
| 3 – 10       	| Moderate evidence for H~1~    	|
| 1 – 3        	| Anecdotal evidence for H~1~    	|
| 1            	| No evidence                  	|
| 1/3 – 1      	| Anecdotal evidence for H~0~   	|
| 1/3 – 1/10   	| Moderate evidence for H~0~    	|
| 1/10 – 1/30  	| Strong evidence for H~0~      	|
| 1/30 – 1/100 	| Very strong evidence for H~0~ 	|
| < 1/100      	| Extreme evidence for H~0~     	|
